\newpage
\section{Discussion and Future Work}
\hl{SECTION UNDER CONSTRUCTION}\\
\iffalse
\hl{State what you've done and what you've found
Summarize contributions (achievements and impact)
Outline open issues/directions for future work
\\\\
The final chapter of the Master's thesis is the Conclusions chapter. Here is where the writer sums up the entire project in one to two brief paragraphs. This chapter should remind the reader of the initial problem statement or hypothesis and then relate that to the results from the study. The writer should then present any conclusions reached or any new insights that arose from this work.  Finally, the writer should present the research in terms of the overall impact in the field. For example, how will the results of this study change the way a person or organization behaves or makes decisions? One caution when writing this chapter is not to merely reiterate the other portions of the thesis. Instead, the writer should strive to leave a lasting impression upon the reader, conveying with the same passion that drove the research project the importance of the work completed.
\\\\
Summary of the problem, the main findings and the discussion. Structured according to the issues in chapter 2.
Comparison with the literature presented in chapter 2: how do your results fill in, advance or contradict previously reported research?
What are the implications of your research for people working in the field that you have studies? In which direction should further research go? }
\fi
